Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-03-31 paper.tex
Add comments about Re dependence of wake generation processes
Add performance description

@@

\todo[inline]{Make sure to use drawing of turbine with no hubs, since these were
included in the tare drag"}

@@

A wake map was generated by positioning a Nortek Vectrino+ acoustic Doppler
Velocimeter (ADV) at 270 different locations, varied in the cross-stream and
vertical directions at one turbine diameter downstream. These locations have
vertical coordinates from the turbine centerline up to $z/H=0.625$, ranging in
the cross-stream direction $y/R = \pm 3$. These locations are show in
Figure~\ref{fig:wake_locations}.

\begin{figure}
\centering
%\includegraphics[width=0.9\textwidth]{figures/turbine_coordinate_system}
\caption{Wake measurement coordinate system and locations. Dimensions are in
meters.} 
\label{fig:wake_locations}
\end{figure}

@@

\todo[inline]{Put up reduced data and processing code on figshare.}

@@

\subsection{Performance Curves}

\todo[inline]{Put the performance curves here.}

\todo[inline]{Put asymptotic behavior here.}

>>>>

We expect that lower lift on the blades at lower $Re$ will weaken tip vortex
shedding, and decrease the levels of turbulence shed from the blade boundary
layers. As mentioned previously, the dynamic stall vortex shedding is not
expected to have a large Reynolds number sensitivity.

@@

\todo[inline]{Make sure to use drawing of turbine with no hubs, since these were
included in the tare drag}

@@

A wake map was generated by positioning a Nortek Vectrino+ acoustic Doppler
Velocimeter (ADV) at 270 different locations, varied in the cross-stream and
vertical directions at one turbine diameter downstream. These locations have
vertical coordinates from the turbine centerline up to $z/H=0.625$, ranging in
the cross-stream direction $y/R = \pm 3$. These locations are shown in
Figure~\ref{fig:wake-locations}.

\begin{figure}
\centering
%\includegraphics[width=0.9\textwidth]{figures/turbine_coordinate_system}
\caption{Wake measurement coordinate system and locations. Dimensions are in
meters.} 
\label{fig:wake-locations}
\end{figure}

@@

\todo[inline]{Cite reduced data and processing code on figshare.}

@@

\subsection{Performance}

Full performance curves for various Reynolds numbers are plotted in
Figure~\ref{fig:perf-curves}.

\todo[inline]{Discuss drag coefficient curves.}

In general, maximum $C_P$ increases with Reynolds number, which is due to an
increase in the foil lift-to-drag ratio. The power coefficient curves also show
a downward shift in the optimal tip speed ratio with increasing Reynolds number.
This is caused by the stall delay from a more turbulent boundary later on the
blade suction side.

\begin{figure}[ht]
\caption{Mean power (left) and drag (right) coefficient curves plotted for
multiple Reynolds numbers.}
\label{fig:perf-curves}
\end{figure}

Mean power and drag coefficients at $\lambda=1.9$ are plotted in
Figure~\ref{fig:perf-Re-dep}

\begin{figure}[ht]
\caption{Mean power (left) and drag (right) coefficients at $\lambda=1.9$
plotted versus Reynolds number.} 
\label{fig:perf-Re-dep}
\end{figure}
